---
title: "Lab 03 - Tidy Graphics and Teamwork"
subtitle: "Due: Sunday, Feb 2 at 11:59pm"
output:
  tufte::tufte_html:
    tufte_variant: "envisioned"
    highlight: pygments
    css: "sta199-labs.css"
link-citations: yes
---

```{r include=FALSE}
knitr::opts_chunk$set(eval = FALSE, comment = "#>")
```

This will be the first team-based lab. Please be sure you are sitting with your
lab group.

# Getting Started

## Clone Assignment Repo

A repository has already been created for you and your teammates. Everyone in
your team has access to the same repository.

- Go to our GitHub course organization page: https://github.com/sta199-sp20-002

- In addition to your private individual repositories, you should now see a
  repository named lab-03-[github_team_name]. Go to that repository.
  
- Each person on the team should now clone the repository into RStudio Cloud.

## Configure git

Remember that we first have to configure RStudio Cloud to talk to GitHub. An 
easy way to do this is to use the `use_git_config()` function from the 
`usethis` package. 

Type the following lines of code in the **`Console`** in RStudio filling in your 
name and email address.

```{r eval=FALSE}
library(usethis)
use_git_config(user.name="Your name", user.email="your-git-hub-email@email.edu")
```

## Password caching

If you would like your git password cached for a week for this project, go to
the **Terminal** tab (next to the **Console** tab) and enter the following at 
the **Terminal's** prompt:

```bash
git config --global credential.helper 'cache --timeout 604800'
```

However, you will need to re-cache your credentials if you open a new project.

## Project name: 

In RStudio Cloud your project is called `Untitled Project`. Update the name of 
your project to be "Lab 03 - Tidy Graphics and Teamwork".

## Packages

In this lab we will work with the `tidyverse` package. 
Load the package with

```{r}
library(tidyverse)
```

# Data

In the **Files** pane you will see a folder named `data`. In it are three
CSV files. Your team will work with data in one of these files according
to the following rule:

| Lab Section         | Data            |
|---------------------|-----------------|
| 04: 1:25p - 2:40p   | `fishing.csv`   |
| 05: 3:05p - 4:20p   | `employees.csv` |
| 06: 4:40p - 5:55p   | `nerrs.csv`     |

CSV files can be read into R using function `read_csv()`. In the function we'll
need to specify where the file is located. We will also want to save the result
so we can work with the data in subsequent steps. For example, if we had a
file named `coronavirus.csv` in the `data` folder, I would read it into R with

```{r eval=FALSE}
coronavirus <- read_csv("data/coronavirus.csv")
```

Eric's Excel files that include the ugly graphic can be found in the folder
named `eric`.

# Using git and GitHub in a team-based environment

The following exercises must be done in order. <b>Only one person should be
pushing at a time.</b>

1. Assign each person on your team a number 1 through 4. For teams of three,
   Member 1 can take on the role of Member 4 in Exercise 5.

2. **Member 1**: Change the author to your team name and include each group
   member's name in the following format: 
   `Team Name: Member 1, Member 2, Member 3, Member 4`. 
   Add code to read in your team's corresponding CSV file and save the result 
   with a meaningful name. Member 1 should stage, commit, and push the changes 
   to GitHub.
   
   - Once Member 1 has pushed their work to GitHub, Members 2, 3, and 4 should
     **Pull** the updated files from the team's GitHub repo. Team members 2, 3,
     and 4 should now have the author information populated in their Rmd file
     and code that reads in the data.
     
   - <b>Make sure you have the most up-date-version of all files before you
     make more changes.</b>
     
3. **Member 2**: Use your assigned data and `ggplot()` to improve the original
   visualization provided by Eric (see the corresponding Excel file in folder
   `eric`). Members 1, 3, and 4 should all provide verbal
   assistance and feedback, but only Member 2 should type the code. Once you
   have a well-labelled visualization, Member 2 should stage, commit, and push 
   the changes to GitHub.
   
   - Once Member 2 has pushed their work to GitHub, Members 1, 3, and 4 should
   **Pull** the updated files from the team's GitHub repo. Team members 1, 3,
   and 4 should now have the code that generates the improved graphic.
   
   - <b>Make sure you have the most up-date-version of all files before you
     make more changes.</b>
   
4. **Member 3**: Include narrative that explains why the original graphic is
   poor. You may want to comment on the labels, figure size, color choices, 
   plot design, and more. Members 1, 2, and 4 should all provide verbal
   assistance and feedback, but only Member 3 should type the narrative.
   Once you have a clear and concise narrative, Member 3 should stage, 
   commit, and push the changes to GitHub.
   
   - Once Member 3 has pushed their work to GitHub, Members 1, 2, and 4 should
   **Pull** the updated files from the team's GitHub repo. Team members 1, 2,
   and 4 should now have the narrative.
   
   - <b>Make sure you have the most up-date-version of all files before you
     make more changes.</b>
   
5. **Member 4**: Include narrative that explains your graphic and why it is an
   improvement over the original visualization. Explain your plot choice given
   the variable types. Members 1, 2, and 3 should all provide verbal
   assistance and feedback, but only Member 4 should type the narrative.
   Once you have a clear and concise narrative, Member 4 should stage, 
   commit, and push the changes to GitHub.
   
   - Once Member 4 has pushed their work to GitHub, Members 1, 2, and 3 should
   **Pull** the updated files from the team's GitHub repo. Team members 1, 2,
   and 3 should now have the narrative.
 
Working in a team typically won't have rules this rigid. However, this is an
introduction to using git and GitHub as a team and we wanted to prevent merge 
conflicts. We'll learn how to handle merge conflicts in the next lab.
   
# Submission

Knit to PDF to create a PDF document. Stage and commit all remaining changes, 
and push your work to GitHub. Make sure all files are updated on your GitHub 
repo.

Please only upload your PDF document to Gradescope. Associate the "Overall"
graded section with the first page of your PDF, and mark where each answer is 
to the exercises. If any answer spans multiple pages, then mark all pages.